Refactoring `nls()`: a constructive critique

### 2023-02-03 RefactoringNLS/JNAB230203.Rmd
add subset section

>>>>

## Feature: Subsetting

`nls()` accepts an argument `subset`. This acts through the mediation of
`model.frame` and is not clearly obvious in the source code files `/src/library/stats/R/nls.R` and 
`/src/library/stats/src/nls.C`.

While the implementation of subset at the level of the call to `nls()` has a certain
attractiveness, it does mean that the programmer of the solver needs to be aware of the
source (and value) of objects such as the data, residuals and Jacobian. This is overly
complicated. By preference, 
we would implement subsetting by means of zero-value weights, with observation counts
(and degrees of freedom) computed via the numbers of non-zero weights. Alternatively,
we would extract a working dataframe from the relevant elements in the original.
